A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-22 ICLP Paper/samplepaper.tex
working on instance format

\subsection{Instance Format}\label{subsec:instance}
% ASP has been applied to solve different scheduling problems. For example, ASP is used to solve scheduling problems in the healthcare systems \cite{dodaro2017nurse,dodaro2019asp}. One of these studies aimed to assign nurses to shifts according to some constraints\cite{dodaro2017nurse}. In addition, ASP has been proposed to solve a train scheduling problem while minimizing the train delay\cite{abels2019train}. One of the limitations of ASP mentioned in these studies is the grounding issues while solving a large number of instances. One of the recent works has presented a multi-shot solving for scheduling problem \cite{francescutto2021solving}. This paper aims to use different decomposition methods to solve the JSP using ASP with Difference Logic. 
% 
% \paragraph{Problem Instances.} 
%
Each job in a JSP instance is a sequence of operations with associated
machines and processing times.
Corresponding facts for an example instance with three jobs and three
machines are displayed in Listing~\ref{prg:facts}.

In order to encode the problem using ASP, we should define a set of predicates that represents the problem instances. For instance, the operations are encoded with the predicate \lstinline{operation/2} where the first variable denotes the job number and the second is the operation number, see lines \ref{prg:facts:ops:begin}-\ref{prg:facts:ops:end} in Listing \ref{prg:facts}. The time needed to finish an operation is represented by the predicate \lstinline{pro/3} in which the operation is determined by the first two terms and the third represents the processing time in lines \ref{prg:facts:pro:begin}-\ref{prg:facts:pro:end}. For the machine assignment, the predicate \lstinline{assign/3} shows that a particular operation is executed by a machine in lines \ref{prg:facts:mach:begin}-\ref{prg:facts:mach:end}. For instance, \emph{operation(1,1)} is processed by machine 2. 
\lstinputlisting[float=bt,mathescape=true,escapeinside={\#(}{\#)},basicstyle={\ttfamily\small},label=prg:facts,caption={Example JSP instance},linerange={1-3}]{listing/facts.lp}

\subsection{Decomposition strategies}
As we mentioned in the previous sections, it is hard to solve the JSP and reach a near-optimal solution in a reasonable time, especially when the number of operations to be processed is high. The decomposition approach has been widely used to solve the JSP by many researchers and proved its efficiency.

>>>>

\subsection{Problem Instances}\label{subsec:instance}
% ASP has been applied to solve different scheduling problems. For example, ASP is used to solve scheduling problems in the healthcare systems \cite{dodaro2017nurse,dodaro2019asp}. One of these studies aimed to assign nurses to shifts according to some constraints\cite{dodaro2017nurse}. In addition, ASP has been proposed to solve a train scheduling problem while minimizing the train delay\cite{abels2019train}. One of the limitations of ASP mentioned in these studies is the grounding issues while solving a large number of instances. One of the recent works has presented a multi-shot solving for scheduling problem \cite{francescutto2021solving}. This paper aims to use different decomposition methods to solve the JSP using ASP with Difference Logic. 
% 
% \paragraph{Problem Instances.} 
%
Each job in a JSP instance is a sequence of operations with associated
machines and processing times.
Corresponding facts for an example instance with three jobs and three
machines are displayed in Listing~\ref{prg:facts}.
An atom of the form
\lstinline{operation(}$j$\lstinline{,}$s$\lstinline{,}$m$\lstinline{,}$p$\lstinline{)}
denotes that the step~$s$ of job~$j$ needs to be processed by machine~$m$ for $p$ time units.
For example, the second operation of job~\lstinline{3} has a processing time of
\lstinline{3} time units on machine~\lstinline{1},
as specified by the fact
\lstinline{operation(3,}\linebreak[1]\lstinline{2,}\linebreak[1]\lstinline{1,3).}
The operation cannot be performed before the first operation of job~\lstinline{3}
is completed,
and its execution must not intersect with the first operation of job~\lstinline{1}
or the second operation of job~\lstinline{2},
which need to be processed by machine~\lstinline{1} as well.
That is, a schedule for the example instance must determine a sequence in which
to process the three mentioned operations on machine~\lstinline{1},
and likewise for operations sharing machine~\lstinline{2} or~\lstinline{3}, respectively.
%
% In order to encode the problem using ASP, we should define a set of predicates that represents the problem instances. For instance, the operations are encoded with the predicate \lstinline{operation/2} where the first variable denotes the job number and the second is the operation number, see lines \ref{prg:facts:ops:begin}-\ref{prg:facts:ops:end} in Listing \ref{prg:facts}. The time needed to finish an operation is represented by the predicate \lstinline{pro/3} in which the operation is determined by the first two terms and the third represents the processing time in lines \ref{prg:facts:pro:begin}-\ref{prg:facts:pro:end}. For the machine assignment, the predicate \lstinline{assign/3} shows that a particular operation is executed by a machine in lines \ref{prg:facts:mach:begin}-\ref{prg:facts:mach:end}. For instance, \emph{operation(1,1)} is processed by machine 2. 
\lstinputlisting[float=bt,mathescape=true,escapeinside={\#(}{\#)},basicstyle={\ttfamily\small},label=prg:facts,caption={Example JSP instance},linerange={1-3}]{listing/facts.lp}

\subsection{Problem Decomposition}\label{subsec:decomposition}
As we mentioned in the previous sections, it is hard to solve the JSP and reach a near-optimal solution in a reasonable time, especially when the number of operations to be processed is high. The decomposition approach has been widely used to solve the JSP by many researchers and proved its efficiency.
